\section{BenchmarkBridge v1}
BenchmarkBridge v1 evaluated the frozen D3 DFM residual gaze-profile model under
internal EyeBench-style split regimes. The run produced participant-by-speech sample
features, deterministic unseen-reader, unseen-text, unseen-reader-plus-text,
text-balanced unseen-reader, leave-one-speech-out, and participant-grouped folds, and
split-specific residualization diagnostics. Held-out reader rows and held-out text rows
were not used for residual fitting in the regimes where they were prohibited, and
reader group was never a residualization predictor.

In reader-aggregated CopCo TYP evaluation, D3 reached AUROC 0.8961 and balanced
accuracy 0.8158 for Unseen Reader, and AUROC 0.8542 and balanced accuracy 0.7458 for
Unseen Reader + Text. Exact official EyeBench folds were not available locally, so
these results are internal benchmark-relative comparisons rather than official
leaderboard results. CopCo RCS was run as an auxiliary target and did not show useful
signal for the main paper story (best reader-aggregated $R^2=0.0116$).

\paragraph{Official EyeBench alignment.}
We additionally vendored the official EyeBench repository and aligned CopCo identifiers, fold metadata, and result formats. Exact official evaluation was not run because the local EyeBench environment did not import and the official processed CopCo files were absent. Accordingly, the benchmark statement remains benchmark-relative rather than an official EyeBench leaderboard or state-of-the-art claim.

\paragraph{Official EyeBench SOTA check.}
OfficialEyeBenchSOTACheck v1 attempted to move the benchmark-relative result to an official EyeBench state-of-the-art claim by creating a clean official EyeBench environment, checking official processed CopCo data, and requiring local reproduction of an official CopCo_TYP baseline before evaluating D3_EyeBench_Lite. The official environment and/or processed data gates did not pass, so the manuscript retains benchmark-relative wording and does not claim official EyeBench SOTA.

\paragraph{Official EyeBench runtime fix.}
OfficialEyeBenchRuntimeFix v1 isolated EyeBench runtime artifacts under the vendored submodule and followed a CopCo-environment-first runtime rule. The CopCo Python 3.11 environment could import the EyeBench package root but failed on Python 3.12-only syntax in the official preprocessing code, so a minimal Python 3.12 prefix was used as a compatibility fallback rather than as an exact environment.yml reproduction. Official CopCo preprocessing then succeeded, producing 57 participants, 452 text items, 4,782 trials, 335,597 word rows, 397,883 fixation rows, and the official folds. D3\_EyeBench\_Lite completed on the official processed data/folds, but its trial-level AUROC/balanced accuracy was 0.8085/0.7274 for Unseen Reader, 0.8319/0.7341 for Unseen Text, and 0.7154/0.6342 for Unseen Reader + Text. A local logistic-regression diagnostic reproduced the published EyeBench logistic values within 0.003, but the official W\&B/tmux command-source baseline was not executed under the isolated runtime. These results do not permit an official EyeBench SOTA claim; the manuscript therefore keeps benchmark-relative wording.

\paragraph{Official EyeBench baseline/evaluator closure.}
OfficialEyeBenchBaselineEvaluatorClosure v1 repaired the minimal Python 3.12 runtime sufficiently to import the official EyeBench ML/evaluator code and attempted the documented CopCo\_TYP LogisticRegressionMLArgs online W\&B command source. The online W\&B sweep lookup failed because no W\&B API key was configured, which is a telemetry/orchestration limitation rather than a scientific blocker. The closure therefore bypassed W\&B and ran a real local official-derived LogisticRegressionMLArgs baseline on the official CopCo\_TYP processed data and official folds. D3\_EyeBench\_Lite did not outperform this local official-derived baseline on the primary trial-level balanced-accuracy comparison, so the manuscript does not claim official EyeBench SOTA and keeps the main benchmark wording conservative.

\paragraph{Operating-point analysis.}
OperatingPointAdaptation v1 re-analyzed existing D3-family prediction probabilities without rerunning leaderboard methods or changing features. Fixed-threshold D3\_EyeBench\_Lite fold-mean trial metrics reproduced the prior official-compatible values, while reader-level probability aggregation preserved stronger secondary AUROC/PR-AUC evidence. Legal threshold learning and fitted calibration were not computed because train/inner-validation calibration predictions were unavailable in the archived artifacts. Test-oracle thresholds were used only as diagnostic upper bounds and are not used for benchmark or SOTA claims.

\paragraph{D3 online targeted optimization.}
D3OnlineTargetedOptimization v1 evaluated D3 as an online sequential detector over prefix evidence from the prepared Label Release v1.1 data. D3 is strongest as an offline reader-profile model. In online sequential detection, probability evidence accumulates across prefixes; targeted calibration, thresholding, and stopping policies provide a deployment-oriented secondary analysis. The analysis keeps oracle rows diagnostic only and does not change the official EyeBench SOTA status.
